PS753 Glossary

### 2022-02-01 _academics/ps753-glossary/ps753-glossary.Rmd
text

vacuously transitive triad
: a triad where (5 of 16 possibilities)

intransitive triad
: a triad where (7 of 16 possibilities)

transitive triad
: a triad where (4 of 16 possibilities)

>>>>

vacuously transitive triad
: a triad where (to be continued...) (5 of 16 possibilities)

intransitive triad
: a triad where (to be continued...) (7 of 16 possibilities)

transitive triad
: a triad where (to be continued...) (4 of 16 possibilities)
